---
title: 'Project 3 : Most Valued Data Science Skills'
author: "Team X"
date: "`r Sys.Date()`"
---

### Load required packages

```{r load-packages, message=FALSE}
library(tidyverse)
library(kableExtra)
library(RMySQL)
library(RODBC)
```

```{r sql_credentials, echo=FALSE}
#user name and password for sql data base connection
usr <- 'dum_usr'
pwd <- 'dum_pwd'
```

### Connect to MYSQL ds_skills schema

```{r}
# Connect to sql server
sql_conn <- dbConnect(MySQL(), user= usr, password = pwd, host='localhost')

# Create schema if does not exist

my_dbname='ds_skills'
MySQLcode <- paste0("CREATE SCHEMA IF NOT EXISTS ",my_dbname,";",sep="")
dbSendQuery(sql_conn, MySQLcode)

# Connect to ds_skills schema
sql_conn <- dbConnect(MySQL(), 
                user = usr,
                password = pwd,
                host = 'localhost',
                dbname = my_dbname)

# Enable local data loading
# We may get below error if it is not enabled
# Loading local data is disabled; this must be enabled on both the client and server sides
MySQLcode <- "SET GLOBAL local_infile=1;"
dbSendQuery(sql_conn, MySQLcode)
```

### Read the data to load into database from github

```{r}
github_url <- "https://raw.githubusercontent.com/Naik-Khyati/p3_607/main/"
```

### Load data into database, read data from database and save it in R dataframe

Read the multipleChoiceResponses spreadsheet from github, upload it as a table into ds_dkills schema and than read the data from newly created database table and save it in a R dataframe

```{r}
file_name <-   "multipleChoiceResponses"
file_url <- paste0(github_url,file_name,".csv",sep='')

# read file
mcr_tb = read.csv(file_url,fill = TRUE)

# Drop table if exists
MySQLcode <- paste0("DROP TABLE IF EXISTS ",file_name,";",sep="")
dbSendQuery(sql_conn, MySQLcode)

# load the spreadsheet into database
dbWriteTable(sql_conn,"multipleChoiceResponses",mcr_tb,row.names = FALSE, overwrite = TRUE)

# load the database table into a R dataframe
multipleChoiceResponses <- dbGetQuery(sql_conn, 'SELECT * FROM multipleChoiceResponses')

dim(multipleChoiceResponses)
```

Read the freeformResponses spreadsheet from github, upload it as a table into ds_dkills schema and than read the data from newly created database table and save it in a R dataframe

```{r}
file_name <-   "freeformResponses"
file_url <- paste0(github_url,file_name,".csv")

# read file
ffr_tb = read.csv(file_url)

# Drop table if exists
MySQLcode <- paste0("DROP TABLE IF EXISTS ",file_name,";",sep="")
dbSendQuery(sql_conn, MySQLcode)

# load the spreadsheet into database
dbWriteTable(sql_conn,"freeformResponses",ffr_tb, row.names = FALSE, overwrite = TRUE)

# load the database table into a R dataframe
freeformResponses <- dbGetQuery(sql_conn, 'SELECT * FROM freeformResponses')

dim(freeformResponses)
```

Read the conversionRates spreadsheet from github, upload it as a table into ds_dkills schema and than read the data from newly created database table and save it in a R dataframe

```{r}
file_name <-   "conversionRates"
file_url <- paste0(github_url,file_name,".csv")

# read file
cr_tb = read.csv(file_url)

# Drop table if exists
MySQLcode <- paste0("DROP TABLE IF EXISTS ",file_name,";",sep="")
dbSendQuery(sql_conn, MySQLcode)

# load the spreadsheet into database
dbWriteTable(sql_conn,"conversionRates",cr_tb, row.names = FALSE, overwrite = TRUE)

# load the database table into a R dataframe
conversionRates <- dbGetQuery(sql_conn, 'SELECT * FROM conversionRates')

dim(conversionRates)
```